---
title: 'Mid Term Exam'
author: 'Tan Somnang'
date: '1/8/2021'
output: html_document
---
1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 & generate another 6x6 matrix (B) using random numbers between 500 to 600.
```{r}
x <- sample(1:100)
y <- sample(500:600)
A <- matrix(x, nrow = 6, ncol = 6)
B <- matrix(y, nrow = 6, ncol = 6)
A
B
```


a. Find the range of matrices A and B.
```{r}
range(A)
range(B)
```

b. Find the max value from each row of the matrices A and B.
```{r}
apply(A,1,max)
apply(B,1,max)

```

c. Find the diagonal values of matrices A&B.
```{r}
z <- A / B
cat('\nTranspose:\n', t(z))
cat('\nDiagonal:\n', diag(t(z)))
```
d. Multiply matrices A and B
```{r}
A %*% B
```
e. Replace the 4th row of Matrix A with diagonal values of matrix B
```{r}
A
A[4, ] <- diag(t(B))
A
```
f. Multiply matrices A & B and store the values on X.
```{r}
X <- A %*% B
X
```
g. Divide the matrix A with matrix B.
```{r}
A / B
```
2. Create a table using dataframe/tibble with the following categories(a to f)
a. First name,
```{r}
FirstName <- c('Somnang','Thavin','Jonh','Phea','Sokha','Sothun','Pisey','Sokheang','Sareth','Kosal')
```

b. Second Name,
```{r}
LastName <- c('Tan','Voeun','Doe','So','Chea','Thea','Seang','Chhun','Neuo','Suy')
```

c. Age,
```{r}
Age<-c(18,23,25,21,12,29,24,10,30,29)
```

d. Occupation,
```{r}
Occupation <- c('Student','Officer','Lawyer','Developer','API Specialist','DevOps','Backend','UI/UX','Frontend','Developer')
```

e. Place,
```{r}
Place <- c('Phnom Penh','Siem Reap','Kompot','Kep','Kampong Thom','Kampong Cham','Siem Reap','Battambang','Phnom Penh','Kep')
```

f. Random numbers( between 1 to 10)
```{r}
RandNumber <- sample(1:10)
```

g. Extract the last column (f)

```{r}
data <- data.frame(FirstName= FirstName, LastName = LastName, Age = Age, Occupation = Occupation, Place = Place, RandomNumber = RandNumber)
data
LastCol <- data[,ncol(data)]

```

h. Find the sum, mean and length of the extracted column
```{r}
sum(LastCol)
mean(LastCol)
length(LastCol)
```
3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from the official news agency’s website(Note: Include the reference link) and do the following

The Phnom Penh Post News: https://www.phnompenhpost.com/national/ministry-review-bill-sewage-wastewater

a. Read the .txt file
```{r}
txt_file <- read.delim('phnompenhpost.txt')
```

b. Perform the Tokenization & count the words
```{r}
words <- paste(txt_file)
tokens <- tokenize_words(words)
count <- count_words(words)
print(count)
```

c. Identify the most repeated word and replace that word with “KIT”
```{r}
most_repeat <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
repeat_count <- max(table(tokens))
subs <- gsub(most_repeat, "KIT", tokens)
most_repeat
repeat_count
subs
```


3. Find the assigned Dataset from the list below and perform the following
a. Import and Clean the dataset.
```{r}
dataset <- read_csv('adjusted-name-combinations-list.csv')
missing = colnames(dataset)[ apply(dataset, 2, anyNA) ]
missing
```
The dataset is cleaned, no missing

b. Find the x and y variables(axis) from the assigned dataset and give the reason for
selecting the x and y axis.

x is adjustment and y is surname, because we can see which surname has the highest or lowest adjustment rate
```{r}
graph <- ggplot(dataset, aes(x = Adjustment, y = Surname)) + 
    xlab("Adjustment") + ylab("Surname")
```

c. Plot the graph using geom_col() and perform the linear model in statistics.
```{r}
graph <- graph + geom_col()
graph<- graph + geom_smooth(method="lm")
graph

```

d. Perform the facet with the available columns(Choose the any two variables from the
columns)
```{r}
graph + facet_grid(FirstName~Surname)
graph <- graph + facet_wrap(~Surname)
graph

```

e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis & graph)
e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space
between graph and title = 20.
e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space
between graph and title = 20.
e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space
between graph and title = 25.

```{r}
graph <- graph +
  ggtitle("Rate of Name Combination List") + theme(
  axis.title.x=element_text(size=10, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
  axis.title.y=element_text(size=10, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
  plot.title=element_text(size=25, color="blue", face="bold", margin=margin(t=25,r=0,b=25,l=0))
  )
graph
```

